---
title: "RWorksheet_Eusuya#4C"
author: "Jonjeryl M. Eusuya"
date: "2024-11-04"
output: pdf_document
---

# 1
# A
```{r}
mpgdata <- read.csv("/cloud/project/RWorksheet_Eusuya#4C/mpg.csv")
mpgdata
```
# B - Which variables from mpg dataset are categorical?
# Datasets that are categorical in mpg are: manufacturer, model, trans, drv, fl and class.

# C - Which are continuous variables?
# Datasets that are continuous in mpg are: displ, year, cyl, cty and hwy

# 2
# A
```{r}
library(dplyr)
library(ggplot2)


manu_count <- mpg %>%
  group_by(manufacturer) %>%
  summarise(model_count = n_distinct(model)) %>%
  arrange(desc(model_count))

top_manu <- manu_count[1, ]

model_var <- mpg %>%
  group_by(model) %>%
  summarise(variation_count = n()) %>%
  arrange(desc(variation_count))

top_model <- model_var[1, ]

top_manu
top_model
```
# A
```{r}
  mile <- mpg %>%
  group_by(manufacturer) %>%
  summarise(unique_models = n_distinct(model)) %>%
  arrange(desc(unique_models))
mile
```
# B
```{r}
library(dplyr)
barplot(mile$unique_models, 
        names.arg = mile$manufacturer, 
        col = "blue",
        main = "Unique Models per Manufacturer", 
        xlab = "Manufacturer", 
        ylab = "Number of Unique Models",
        las = 2,          
        cex.names = 0.7)
```
```{r}
library(ggplot2)

ggplot(mile, aes(x = manufacturer, y = unique_models)) +
  geom_bar(stat = "identity", fill = "blue") +
  ggtitle("Unique Models per Manufacturer") +
  xlab("Manufacturer") +
  ylab("Number of Unique Models") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 10))  
```

# 2.2
# A
```{r}
ggplot(mpgdata, aes(model, manufacturer)) + geom_point()
```
# The ggplot shows the manufacturer and the model of the car they made.

# B - For you, is it useful? If not, how could you modify the data to make it more informative?
# No the data is not useful. I would make the model names clearer to make the ggplot useful.

# 3
```{r}
library(ggplot2)
library(dplyr)

mpg_top20 <- mpg %>% head(20)

ggplot(mpg_top20, aes(x = model, y = year)) +
  geom_point(color = "blue", size = 3) +
  labs(title = " Model vs Year", 
       x = "Model", 
       y = "Year") +
  theme_minimal()
```
# 4
```{r}
library(dplyr)
library(ggplot2)

cars_per_model <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))
cars_per_model
```
# A
```{r}
library(ggplot2)
library(dplyr)

mpg_top20 <- mpg %>% head(20)
model_counts <- mpg_top20 %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))

ggplot(model_counts, aes(x = reorder(model, -car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  labs(title = "Cars per Model",
       x = "Car Model", 
       y = "Number of Cars") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_manual(values = rainbow(nrow(model_counts)))
```
# B
```{r}
library(ggplot2)
library(dplyr)

model_counts <- mpg %>%
  group_by(model) %>%
  summarise(car_count = n()) %>%
  arrange(desc(car_count))
ggplot(model_counts, aes(x = reorder(model, car_count), y = car_count, fill = model)) +
  geom_bar(stat = "identity") +
  coord_flip() +
  labs(title = "Cars per Model", 
       x = "Car Model", 
       y = "Number of Cars") +
  theme_minimal() +
  theme(legend.position = "none") + 
  scale_fill_manual(values = rainbow(nrow(model_counts)))
```
# 5
```{r}
library(ggplot2)

ggplot(mpg, aes(x = cyl, y = displ, color = displ)) +
  geom_point(size = 3) +
  labs(title = "Relationship between No. of Cylinders and Engine Displacement",
       x = "Number of Cylinders",
       y = "Engine Displacement",
       color = "Engine Displacement") +
  theme_minimal()
```
# A - How would you describe its relationship?
# When the number of cylinders increase the engine displacement also increases.

# 6
```{r}
library(ggplot2)

ggplot(mpg, aes(x = displ, y = hwy, color = displ)) +
  geom_point(size = 3, alpha = 0.7) +
  labs(title = "Relationship between Engine Displacement and Highway Miles per Galon",
       x = "Engine Displacement",
       y = "Highway Miles per Gallon",
       color = "Engine Displacement") +
  theme_minimal()
```
# 6.2
```{r}
traffic_data <- read.csv("/cloud/project/RWorksheet_Eusuya#4C/traffic.csv")
traffic_data
```
# A
```{r}
observations <- nrow(traffic_data)
print(paste("Number of observations:", observations))

variables <- colnames(traffic_data)
print(paste("Variables:", variables))
```
# B
```{r}
junctions <- split(traffic_data, traffic_data$Junction)
junctions
```
# C
```{r}
library(ggplot2)
library(dplyr)

traffic_data$DateTime <- as.POSIXct(traffic_data$DateTime, format="%Y-%m-%d %H:%M:%S")
ggplot(traffic_data, aes(x = DateTime, y = Vehicles, color = factor(Junction))) +
  geom_line() +
  labs(title = "Traffic Volume",
       x = "Date and Time",
       y = "Number of Vehicles",
       color = "Junction") +
  theme_minimal() +
  facet_wrap(~ Junction, scales = "free_y")
```
# 7
```{r}
library(readxl)
alexa_data <- read_excel("/cloud/project/RWorksheet_Eusuya#4C/alexa_file.xlsx")
alexa_data
```
# A
```{r}
observations2 <- nrow(alexa_data)
print(paste("Number of observations:", observations2))

variables2 <- colnames(alexa_data)
print(paste("Variables:", variables2))
```
# B
```{r}
library(dplyr)

variation_counts <- alexa_data %>%
  group_by(variation) %>%
  summarise(total = n())
print(variation_counts)
```
# C
```{r}
ggplot(variation_counts, aes(x = reorder(variation, -total), y = total, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Of Each Variations",
       x = "Product Variation",
       y = "Number of Variation") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE)
```
# D
```{r}
alexa_data$date <- as.Date(alexa_data$date)

daily_reviews <- alexa_data %>%
  group_by(date) %>%
  summarise(total_verified_reviews = sum(feedback))

ggplot(daily_reviews, aes(x = date, y = total_verified_reviews)) +
  geom_line(color = "blue") +
  labs(title = "Number of Verified Reviews",
       x = "Date",
       y = "Verified Reviews") +
  theme_minimal()
```
# E
```{r}
library(dplyr)
library(ggplot2)

ratings <- alexa_data %>%
  group_by(variation) %>%
  summarise(average_rating = mean(rating, na.rm = TRUE)) %>%

arrange(desc(average_rating))
ratings
```
```{r}
ggplot(ratings, aes(x = reorder(variation, -average_rating), y = average_rating, fill = variation)) +
  geom_bar(stat = "identity") +
  labs(title = "Product Variations and Ratings",
       x = "Product Variation",
       y = "Average Rating") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  guides(fill = FALSE)
```


